Outline paper - Multiple imputation for statistical disclosure control: Creating synthetic datasets with *mice*

### 2021-10-04 mice_synthesizing/paper.Rmd
Update paper and .gitignore file.

---
title: "Outline paper - Multiple imputation for statistical disclosure control: Creating synthetic datasets with *mice*"
subtitle: "Anony*mice*d shareable data: Using *mice* to create multiply imputed synthetic datasets" 
author:
- Thom Volker & Gerko Vink
date: "`r format(Sys.time(), '%d-%m-%Y')`"
output: 
  html_document:
    theme: spacelab
    highlight: tango
    toc: true
    toc_depth: 2
    toc_float: true
    number_sections: true
bibliography: federated_imp.bib
csl: "apa-6th-edition.csl"
---

>>>>

---
title: "Outline paper - Multiple imputation for statistical disclosure control: Creating synthetic datasets with *mice*"
subtitle: "Anony*mice*d shareable data: Using *mice* to create multiply imputed synthetic datasets" 
author:
- Thom Volker^[Helpful and stimulating discussions with Stef van Buuren, Hanne Oberman, Paulina von Stackelberg, Mirthe Hendriks and Stijn Overbeek are gratefully acknowledged.] & Gerko Vink
date: "`r format(Sys.time(), '%d-%m-%Y')`"
output: 
  html_document:
    theme: spacelab
    highlight: tango
    toc: true
    toc_depth: 2
    toc_float: true
    number_sections: true
bibliography: federated_imp.bib
csl: "apa-6th-edition.csl"
---
